Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-08-18 Papers/InProgress/NaturalDeduction/GodProof-ND.tex

Double lines are used to abbreviate tedious propositional reasoning steps in the derivations. Dashed lines are used to refer to an axiom or theorem with the proof shown elsewhere. When proof trees are too large to fit on the page, some branches may be displayed separately. In such cases, the conclusion of the branch and the location in the main proof tree where the branch belongs are annotated with the same symbol (a subscripted $\subproof$). Dotted lines are used to indicate folding and unfolding of definitions. Furthermore, as it is inconvenient to draw boxes around large derivations in \LaTeX, formulas inside boxes are labeled with the names of the boxes surrounding them. Therefore, the boxes can be omitted without loss of information.

@@

@@

In this section, natural deduction proofs of three convenient derived modal principles are presented. These principles are used in the ontological proofs formalized in the next sections. Although they are well-known among modal logicians, we include their proofs here in order to have a self-contained and fully formal presentation of the ontological proofs, without any gaps.

>>>>

Double lines are used to abbreviate tedious propositional reasoning steps in the derivations where the reasoning is otherwise clear. Dashed lines are used to refer to an axiom or theorem with the proof shown elsewhere. When proof trees are too large to fit on the page, some branches may be displayed separately. In such cases, the conclusion of the branch and the location in the main proof tree where the branch belongs are annotated with the same symbol (a subscripted $\subproof$). Dotted lines are used to indicate folding and unfolding of definitions. Furthermore, as it is inconvenient to draw boxes around large derivations in \LaTeX, formulas inside boxes are labeled with the names of the boxes surrounding them. Therefore, the boxes can be omitted without loss of information.

@@

\begin{calculus}
{Equality rules}
{fig:EqualityRules}

\s\s\s\s
\infer[Ref]{t=t}{}
\s\s
\infer[Sym]{s=t}{ t=s }
\s\s
\infer[Trans]{s=t}{s=u & u=t}

@@

In this section, natural deduction proofs of three convenient derived modal principles are presented. These principles are used in the ontological proofs formalized in the next sections. Although they are well-known among modal logicians, we include their proofs here in order to have a self-contained and fully formal presentation of the ontological proofs.
